---
title: "AirbnbReport"
author: BDA Group
date: "6 February 2016"
output: html_document
---

Airbnb Booking Analysis
==========================================

**BDA** - *INSEAD MBA 16J*


 
## Business motivation

Understanding customers' dynamics and behaviour is essential for digital companies, especially for those whose business model is based on purchases or reservations from customers. 

In the case of a company such as Airbnb, where customers rent rooms or apartments from other users, it is key to understand what drives customers to make the final reservation. If the company manages to understand the patterns, and has a systematic process to analyze the behaviour, it will be able to implement actions to improve the booking ratio, as well as to assess the success of the actions. 

For this case, we have selected a public shared file with data from customers, and we will guide you through the different data that the file contains, and the different measures that we find interesting in order to analyze customers' behaviour. 

The raw data file is sourced from airbnb website and contains data from May 2014 to May 2015. It is publically available data put up by airbnb as a part of an analytics competition.

It is very important to understand the columns, let's review its content:

* **id_visitor**: the id of the visitor
* **id_session**: the id of the session
* **dim_session_number**: the number of session on a given day for a visitor
* **dim_user_agent**: the user agent of the session
* **dim_device_app_combo**: the parsed out device/app combo from user agent
* **ds**: date stamp of session
* **ts_min**: time of session start
* **ts_max**: time of session end
* **did_search**: binary flag indicating if the visitor performed a search during the session
* **sent_message**: binary flag indicating if the visitor sent a message during the session
* **sent_booking_request**: binary flag indicating if the visitor sent a booking request during the session


<br>

Let us look at the data in available form. We have taken first hundred rows of data to display the data:
<br>

```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
library(googleVis)
library(dplyr)
local_directory <- getwd()
ProjectData <- read.csv("../data/Airbnb_data1.csv", sep=",", dec=".") # this contains only the matrix ProjectData
t1 <- gvisTable(ProjectData[1:100,],options = list(showRowNumber = FALSE, width = 800, height = min(400,27*(nrow(ProjectData) + 1)), allowHTML = TRUE, page = 'disable'))
print(t1,'chart')
```

# Conversion rates

Let's have a look at the conversion rates for the users. We are going to analyze in this case several ratios, such as:
- the percentage of visits that end in bookings
- the percentage of times that users send a message to the owner
- the perc. of times that a booking is realized after a message has been sent

Before any other analysis, let's look at these ratios (Each block of code corresponds to one ratio) for the global set of customers (without considering the number of session or other parameters):

```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
int1 <- ProjectData[ProjectData$sent_booking_request == 1,]
int2 <- select(int1, totalbookings = sum(sent_booking_request))
int3 <- summarise(int2, percbookings = sum(totalbookings)*100/nrow(ProjectData))
numbookings <- paste(round(int3$percbookings, digits = 2), "%", sep="")

int4 <- ProjectData[ProjectData$sent_message == 1,]
int5 <- select(int4, totalmessages = sum(sent_message))
int6 <- summarise(int5, percmessage = sum(totalmessages)*100/nrow(ProjectData))
nummessages <- paste(round(int6$percmessage, digits = 2), "%", sep="")

int7 <- int4[int4$sent_booking_request == 1,]
int8 <- select(int7, subbookings = sum(sent_booking_request))
int9 <- summarise(int8, percmessage = sum(subbookings)*100/nrow(int4))
numbookings2 <- paste(round(int9$percmessage, digits = 2), "%", sep="")
```

**Summary**

- Percentage of visits that end in bookings: `r numbookings`

- Percentage of times user send a message: `r nummessages`

- Percentage of times user booked after a message: `r numbookings2`

<br>
As we can see, for every 100 visits to Airbnb, only less than 2 end up in a booking. Although we can't conclude whether this figure is high or low, it will be interesting to keep a record of how this percentage change along time, and whether it changes with specific actions Airbnb takes in marketing.
<br>
On the other hand, if we check the success ratio after sending a message, we can see it is much higher than without a message (for every 100 messages sent, over 8 bookings were realized). It would be useful to have more data about what it is that drives the customers to send messages. 
<br>
If Airbnb could gather the information about why customers send messages, it could develop more targeted campaigns, and could track whether the ratio of messages vs visits increases, and/or whether the ratio of bookings vs messages increases.

<br>

##Seasonility, visitor and device analysis 
In the following we will visually analyze the data by date, unique visitor and device. This helps Airbnb to get a better intuition about who their customers are and how they behave. In the following we will visualize data along the date line, unique visitors and devices/app from which they accessed Airbnb.



```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
# Here we add further columns to the ProjecData and change the data class for some. i.e. start date, end date, time difference, and entrance, as flag.

ProjectData[,"ts_min_calc"]=dmy_hm(ProjectData[,which(colnames(ProjectData)=="ts_min")])
ProjectData[,"ts_max_calc"]=dmy_hm(ProjectData[,which(colnames(ProjectData)=="ts_max")])
ProjectData[,"ts_diff"]=difftime(ProjectData[,which(colnames(ProjectData)=="ts_max_calc")],ProjectData[,which(colnames(ProjectData)=="ts_min_calc")])
ProjectData[,"ts_min_date"]=as.Date(ProjectData[,which(colnames(ProjectData)=="ts_min_calc")])
ProjectData[,"ts_max_date"]=as.Date(ProjectData[,which(colnames(ProjectData)=="ts_max_calc")])
ProjectData[,"sameday_check"]=ifelse(ProjectData$ts_min_date==ProjectData$ts_max_date,0,1)
ProjectData[,"entrance"]=1

# Here we create the dynamic start and end date of the data set. 
startDate=as.Date(min(ProjectData$ts_min_calc))
endDate=as.Date(max(ProjectData$ts_max_calc))
```


```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
#by Visitors: pulling  the relevant data together from the main data.frame and ordering it by unique visitor (for visits, bookings, searches, messages and average session duration)
VisitsbyVisitor = aggregate.data.frame(ProjectData$entrance, by = list(ProjectData$id_visitor), FUN=sum)
  VisitsbyVisitor[,"unique_visitor"] = as.character(VisitsbyVisitor$Group.1)
  VisitsbyVisitor[,"visits"] = as.numeric(VisitsbyVisitor$x)
  VisitsbyVisitor$Group.1 = NULL
  VisitsbyVisitor$x = NULL

BookingsbyVisitor = aggregate.data.frame(ProjectData$sent_booking_request, by = list(ProjectData$id_visitor), FUN=sum)
  BookingsbyVisitor[,"unique_visitor"] = as.character(BookingsbyVisitor$Group.1)
  BookingsbyVisitor[,"bookings"] = as.numeric(BookingsbyVisitor$x)
  BookingsbyVisitor$Group.1 = NULL
  BookingsbyVisitor$x = NULL

SearchesbyVisitor = aggregate.data.frame(ProjectData$did_search, by = list(ProjectData$id_visitor), FUN=sum)
  SearchesbyVisitor[,"unique_visitor"] = as.character(SearchesbyVisitor$Group.1)
  SearchesbyVisitor[,"searches"] = as.numeric(SearchesbyVisitor$x)
  SearchesbyVisitor$Group.1 = NULL
  SearchesbyVisitor$x = NULL

MessagesbyVisitor = aggregate.data.frame(ProjectData$sent_message, by = list(ProjectData$id_visitor), FUN=sum)
  MessagesbyVisitor[,"unique_visitor"] = as.character(MessagesbyVisitor$Group.1)
  MessagesbyVisitor[,"messages"] = as.numeric(MessagesbyVisitor$x)
  MessagesbyVisitor$Group.1 = NULL
  MessagesbyVisitor$x = NULL

TimebyVisitor = aggregate.data.frame(ProjectData$ts_diff, by = list(ProjectData$id_visitor), FUN=sum)
  TimebyVisitor[,"unique_visitor"] = as.character(TimebyVisitor$Group.1)
  TimebyVisitor[,"avg_sess_dur_mins"] = round(as.numeric(TimebyVisitor$x / VisitsbyVisitor$visits / 60), 2)
  TimebyVisitor$Group.1 = NULL
  TimebyVisitor$x = NULL

# Here we merge all the subsets of ordere data into one data.frame used for the analysis
byVisitor = join(VisitsbyVisitor, BookingsbyVisitor)
  byVisitor = join(byVisitor, SearchesbyVisitor)
  byVisitor = join(byVisitor, MessagesbyVisitor)
  byVisitor = join(byVisitor, TimebyVisitor)

```



```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
#by Date: pulling  the relevant data together from the main data.frame and ordering it by date (for visits, bookings, searches, messages and average session duration)
Date=as.data.frame(as.Date(c(startDate:endDate), origin = "1970-01-01"))
rownames(Date) = c(as.Date(c(startDate:endDate), origin = "1970-01-01"))
colnames(Date) = c("date")

VisitsbyDate = aggregate.data.frame(ProjectData$entrance, by = list(ProjectData$ts_min_date), FUN=sum)
  VisitsbyDate[,"date"] = as.Date(VisitsbyDate$Group.1)
  VisitsbyDate[,"visits"] = as.numeric(VisitsbyDate$x)
  VisitsbyDate$Group.1 = NULL
  VisitsbyDate$x = NULL

BookingsbyDate = aggregate.data.frame(ProjectData$sent_booking_request, by = list(ProjectData$ts_min_date), FUN=sum)
  BookingsbyDate[,"date"] = as.Date(BookingsbyDate$Group.1)
  BookingsbyDate[,"bookings"] = as.numeric(BookingsbyDate$x)
  BookingsbyDate$Group.1 = NULL
  BookingsbyDate$x = NULL

SearchesbyDate = aggregate.data.frame(ProjectData$did_search, by = list(ProjectData$ts_min_date), FUN=sum)
  SearchesbyDate[,"date"] = as.Date(SearchesbyDate$Group.1)
  SearchesbyDate[,"searches"] = as.numeric(SearchesbyDate$x)
  SearchesbyDate$Group.1 = NULL
  SearchesbyDate$x = NULL

MessagesbyDate = aggregate.data.frame(ProjectData$sent_message, by = list(ProjectData$ts_min_date), FUN=sum)
  MessagesbyDate[,"date"] = as.Date(MessagesbyDate$Group.1)
  MessagesbyDate[,"messages"] = as.numeric(MessagesbyDate$x)
  MessagesbyDate$Group.1 = NULL
  MessagesbyDate$x = NULL

TimebyDate = aggregate.data.frame(ProjectData$ts_diff, by = list(ProjectData$ts_min_date), FUN=sum)
  TimebyDate[,"date"] = as.Date(TimebyDate$Group.1)
  TimebyDate[,"avg_sess_dur_mins"] = round(as.numeric(TimebyDate$x / VisitsbyDate$visits / 60), 2)
  TimebyDate$Group.1 = NULL
  TimebyDate$x = NULL

# Here we merge all the subsets of ordered data into one data.frame used for the analysis and formate the date column to class = date
byDate = join(Date, VisitsbyDate)
  byDate = join(byDate, BookingsbyDate)
  byDate = join(byDate, SearchesbyDate)
  byDate = join(byDate, MessagesbyDate)
  byDate = join(byDate, TimebyDate)
  byDate[,"date"] = as.Date(Date$date)

```


```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
#by device: pulling  the relevant data together from the main data.frame and ordering it by device and app (for visits, bookings, searches)
VisitsbyDevice = aggregate.data.frame(ProjectData$entrance, by = list(ProjectData$dim_device_app_combo), FUN = sum)
  VisitsbyDevice[,"Device_App"] = as.character(VisitsbyDevice$Group.1)
  VisitsbyDevice[,"visits"] = as.numeric(VisitsbyDevice$x)
  VisitsbyDevice$Group.1 = NULL
  VisitsbyDevice$x = NULL

BookingsbyDevice = aggregate.data.frame(ProjectData$sent_booking_request, by = list(ProjectData$dim_device_app_combo), FUN = sum)
  BookingsbyDevice[,"Device_App"] = as.character(BookingsbyDevice$Group.1)
  BookingsbyDevice[,"bookings"] = as.numeric(BookingsbyDevice$x)
  BookingsbyDevice$Group.1 = NULL
  BookingsbyDevice$x = NULL

SearchesbyDevice = aggregate.data.frame(ProjectData$did_search, by = list(ProjectData$dim_device_app_combo), FUN = sum)
  SearchesbyDevice[,"Device_App"] = as.character(SearchesbyDevice$Group.1)
  SearchesbyDevice[,"searches"] = as.numeric(SearchesbyDevice$x)
  SearchesbyDevice$Group.1 = NULL
  SearchesbyDevice$x = NULL

MessagesbyDevice = aggregate.data.frame(ProjectData$sent_message, by = list(ProjectData$dim_device_app_combo), FUN = sum)
  MessagesbyDevice[,"Device_App"] = as.character(MessagesbyDevice$Group.1)
  MessagesbyDevice[,"messages"] = as.numeric(MessagesbyDevice$x)
  MessagesbyDevice$Group.1 = NULL
  MessagesbyDevice$x = NULL

# Here we merge all the subsets of ordered data into one data.frame used for the analysis
byDevice = join(VisitsbyDevice, BookingsbyDevice)
  byDevice = join(byDevice, SearchesbyDevice)
 byDevice = join(byDevice, MessagesbyDevice)

#cleaning up the environment with all the sub data.frames that were merged into the three groups byDate, byVisitor, and by Device
rm(VisitsbyDevice,VisitsbyDate,VisitsbyVisitor,BookingsbyDevice,BookingsbyDate,BookingsbyVisitor,SearchesbyDevice,SearchesbyDate,SearchesbyVisitor,MessagesbyDevice,MessagesbyDate,MessagesbyVisitor,TimebyDate,TimebyVisitor)
```
<br>
<br>

## Visualization of data by date

<br>
Here we grouped all data by date with the goal to see whether we can identify any seasonal trends with regards to customer activity. 
<br>
First let's look at the data sorted by date, between `r startDate` and `r endDate`. Below are the first 10 entries:
<br>
<br>
```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis', fig.align="center"}
td1 <- gvisTable(byDate[1:10,],options = list(showRowNumber = FALSE, width = 1920, height = min(400,27*(nrow(byDate) + 1)), allowHTML = TRUE, page = 'disable', margin))
print(td1,'chart')
```
<br>
<br>
Looking at the data we see spikes in activity around September, as well as the end of the year and early February. It is interesting to see that while there seems to be some seasonality effect with the number of visits this does not fully translate in a similar pattern for the number of searches.
<br>
<br>
```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis', fig.align="center", warning=FALSE}
ggplot(byDate, aes(x = byDate$Date, y = byDate$visits)) + geom_area(data = byDate, aes(x = date, y = visits, fill = "Visits"), stat = "identity") + theme_minimal() + ylab("# of Counts") + xlab("Date") + theme(axis.text.x=element_text(angle = 45, vjust = .5)) + ggtitle("# Visits & Searches by Date") + scale_x_date(limits = c(startDate, endDate), date_breaks = "3 weeks") + scale_y_discrete(breaks = pretty_breaks(n=5)) + geom_area(data = byDate, aes(x = date, y = searches, fill = "Searches")) + labs(fill="", colour="")
```
<br>
<br>
A similar pattern also holds for messages and bookings which are relatively evenly spread throughout the year.
<br>
<br>
```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis', fig.align="center", warning=FALSE}
ggplot(byDate, aes(x = byDate$Date, y = byDate$visits)) + geom_area(data = byDate, aes(x = date, y = messages, fill = "Messages"), stat = "identity", size = 0.5) + geom_area(data = byDate, aes(x = date, y = bookings, fill = "Bookings"), stat = "identity", size = 0.5) + theme_minimal() + ylab("# of Counts") + xlab("Date") + theme(axis.text.x=element_text(angle = 45, vjust = .5)) + ggtitle("# Messages & Bookings by Date") + scale_x_date(limits = c(startDate, endDate), date_breaks = "3 weeks") + scale_y_discrete(breaks = pretty_breaks(n=5)) + labs(fill="")
```
<br>
<br>
However, the average session duration was significantly higher around September than other times of the year. Further research needs to be done in order to completely understand this spike.
<br>
<br>
```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis', fig.align="center", warning=FALSE}
ggplot(byDate, aes(x = byDate$Date, y = byDate$visits)) + geom_bar(data = byDate, aes(x = date, y = avg_sess_dur_mins, fill = "Session Duration"), stat = "identity", size = 0.5) + theme_minimal() + ylab("Minutes") + xlab("Date") + theme(axis.text.x=element_text(angle = 45, vjust = .5)) + ggtitle("Average Session Duration by Date") + scale_x_date(limits = c(startDate, endDate), date_breaks = "3 weeks") + scale_y_discrete(breaks = pretty_breaks(n=5)) + labs(fill="")
```
<br>
<br>
<br>
<br>
<br>

## Visualization of data by unique visitor

<br>
Let's have a look at the first 10 entries of the data by unique visitor:
<br>
<br>
```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis', fig.align='center'}
td1 <- gvisTable(byVisitor[1:10,],options = list(showRowNumber = FALSE, width = 1920, height = min(400,27*(nrow(byVisitor) + 1)), allowHTML = TRUE, page = 'disable'), )
print(td1,'chart')
```
<br>
<br>
Here we see that only a very small part of all unique visitors account for the majority share of all visits. Yet the number of searches is driven by a broader unique visitor base. 
<br>
<br>
```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis', fig.align="center", warning=FALSE}
ggplot(byVisitor, aes(x = reorder(byVisitor$unique_visitor,-byVisitor$visits), y = byVisitor$visits)) + geom_bar(stat = "identity", aes(fill = "Visits")) + theme_minimal() + ylab("# of Counts") + xlab("Unique Visitors") + theme(axis.text.x=element_text(angle = 45, vjust = .5)) + ggtitle("# Visits & Searches by Unique Visitor") + scale_x_discrete(breaks = pretty_breaks(n=7)) + scale_y_discrete(breaks = pretty_breaks(n=5)) + geom_bar(data=byVisitor, aes(x = unique_visitor, y = searches, fill = "Searches"), stat = "identity") + labs(fill="", colour="")
```
<br>
<br>
Below we see the Searches, Messages and Bookings by Unique Visitors.
<br>
<br>
```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis', fig.align="center", warning=FALSE}
ggplot(byVisitor, aes(x = reorder(byVisitor$unique_visitor,-byVisitor$visits), y = byVisitor$visits)) + geom_bar(data=byVisitor, stat = "identity", aes(y=messages, fill = "Messages"), position = "dodge") + theme_minimal() + ylab("# of Counts") + xlab("Unique Visitors (ordered by # of Visits)") + theme(axis.text.x=element_text(angle = 45, vjust = .5)) + ggtitle("# Searches, Messages and Bookings by Unique Visitors") + scale_x_discrete(breaks = pretty_breaks(n=7)) + scale_y_discrete(breaks = pretty_breaks(n=5)) + geom_bar(data=byVisitor, aes(x = unique_visitor, y = searches, fill = "Searches"), position = "dodge", stat = "identity") + geom_bar(data=byVisitor, aes(x = unique_visitor, y = bookings, fill = "Bookings"), position = "dodge", stat = "identity") + labs(fill="", colour="")
```
<br>
<br>
Below we show the average time unique visitors spent per session.
<br>
<br>
```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis', fig.align="center", warning=FALSE}
ggplot(byVisitor, aes(x = reorder(byVisitor$unique_visitor,-byVisitor$visits), y = byVisitor$visits)) + geom_bar(data=byVisitor, stat = "identity", aes(y=avg_sess_dur_mins, fill = "Session Duration"), position = "dodge") + theme_minimal() + ylab("Minutes") + xlab("Unique Visitors (ordered by # of Visits)") + theme(axis.text.x=element_text(angle = 45, vjust = .5)) + ggtitle("Average Session Duration by Unique Visitor") + scale_x_discrete(breaks = pretty_breaks(n=7)) + scale_y_discrete(breaks = pretty_breaks(n=5)) + labs(fill="", colour="")
```


## Visualization of data by by device

<br>

Lastly, let's have a look at the data by device and app from which the customers accessed Airbnb.
<br>
<br>

```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis', fig.align="center"}
td1 <- gvisTable(byDevice[1:10,],options = list(showRowNumber = FALSE, width = 1920, height = min(400,27*(nrow(byDevice) + 1)), allowHTML = TRUE, page = 'disable'))
print(td1,'chart')
```
<br>
<br>
Below you can find the graphical output of our data analysis by device and app. We see that most people access Airbnb from the Iphones apps. Access via desktop also relatively wide spread, however, Android users are less active, or form a smaller part of Airbnb users.
<br>
<br>
```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis', fig.align="center"}
ggplot(byDevice, aes(x = reorder(byDevice$Device_App,-byDevice$visits), y = byDevice$visits)) + geom_bar(stat = "identity", aes(fill = "Visits")) + theme_minimal() + ylab("# of Visits") + xlab("Device & App") + theme(axis.text.x=element_text(angle = 45, vjust = .5)) + ggtitle("# of Visits by Device & App") + labs(fill="")
```
<br>
<br>
Below we see the Searches, Messages and Bookings activity by Device and App.
<br>
<br>
```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis', fig.align="center", warning=FALSE}
ggplot(byDevice, aes(x = reorder(byDevice$Device_App,-byDevice$visits), y = searches)) + geom_bar(data=byDevice, aes(x = Device_App, y = searches, fill = "Searches"), stat = "identity") + theme_minimal() + ylab("# of Counts") + xlab("Devices & App (ordered by # of Visits)") + theme(axis.text.x=element_text(angle = 90, vjust = .5)) + ggtitle("# Searches by Devices & App") + scale_y_discrete(breaks = pretty_breaks(n=5)) + labs(fill="", colour="") + theme(axis.text.x=element_text(angle = 45, vjust = .5))
```
<br>
<br>
```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis', fig.align="center", warning=FALSE}
ggplot(byDevice, aes(x = reorder(byDevice$Device_App,-byDevice$visits), y = messages)) + geom_bar(data=byDevice, aes(x = Device_App, y = messages , fill = "Messages"), stat = "identity") + theme_minimal() + ylab("# of Counts") + xlab("Devices & App (ordered by # of Visits)") + theme(axis.text.x=element_text(angle = 90, vjust = .5)) + ggtitle("# Messages by Devices & App") + scale_y_discrete(breaks = pretty_breaks(n=5)) + labs(fill="", colour="") + theme(axis.text.x=element_text(angle = 45, vjust = .5))
```
<br>
<br>
```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis', fig.align="center", warning=FALSE}
ggplot(byDevice, aes(x = reorder(byDevice$Device_App,-byDevice$visits), y = bookings)) + geom_bar(data=byDevice, aes(x = Device_App, y = bookings , fill = "Bookings"), stat = "identity") + theme_minimal() + ylab("# of Counts") + xlab("Devices & App (ordered by # of Visits)") + theme(axis.text.x=element_text(angle = 90, vjust = .5)) + ggtitle("# Bookings by Devices & App") + scale_y_discrete(breaks = pretty_breaks(n=5)) + labs(fill="", colour="") + theme(axis.text.x=element_text(angle = 45, vjust = .5))
```
<br>
<br>
<br>


##Time analysis


<br>
When we look at the trend in visits by month, we see that September and December have the highest traffic, which is likely being driven by the summer and winter vacation periods.
By day of week, we find that traffic appears to be somewhat higher on weekdays in comparison to weekends. Given that the majority of visits are being done through mobile devices this may be a result of users spending time on Airbnb during their commutes or during breaks in the work day.
In terms of hourly traffic, there is a significant drop in traffic between 3pm-7pm. We do not have enough data to determine the causes, but this suggests that online marketing efforts such as paid-search should be reduced during this time period to optimize cost-benefit. 
<br>


<br>
```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
#chooseCRANmirror(ind=1)
airbnbdata = read_excel("../data/Airbnb_data.xlsx")
dates <- airbnbdata[,"ds"]
dates <- as.matrix(dates)
#dates <- as.Date.POSIXct(dates)
dates_m <- month(dates)
dates_m <- t(t(dates_m))

hist(dates_m, breaks= 0:13, col="lightblue", labels=TRUE, xlim=c(0,12), ylim=c(0,1400), xlab="Month (1=Jan etc)", main="Frequency of sessions by month")
library(ggplot2)
#qplot(dates_m, geom="histogram", binwidth=1)
```

<br>

```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
#Frequency of sessions by day of week (based on start time):
dates_day <- wday(dates)
dates_day <- t(t(dates_day))

dat <- as.Date(dates)
Dayofweek_a <- format(dat , "%a")   #day of week
Dayofweek <- as.numeric( format(dat , "%w") ) # numeric version of day of week
hist(Dayofweek , breaks= -.5+0:7, labels= unique(Dayofweek_a[order(Dayofweek)]), ylim=c(0,1400), main="Number of sessions by day of week")
```

<br>

```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
#Frequency of sessions by hour of day:
dates_min <- airbnbdata[,"ts_min"]
dates_min <- as.matrix(dates_min)
dates_h <- hour(dates_min)
dates_h[dates_h==0] <- 24
dates_h <- t(t(dates_h))
dates_h_forhist <- dates_h + 1
dates_h_forhist[dates_h_forhist==2] <- 1.5

opar=par(ps=10) #this changes the default font size for the graph
hist(dates_h_forhist, breaks=24, col="lightblue", labels=TRUE, xlim=c(0,25), ylim=c(0,750), xaxt="n", main="Number of sessions by hour of day", xlab="Hour of day", cex.main=1.5, cex.axis=1.2, cex.lab=1.2)
axis(side=1, at=seq(0,25,1), labels=seq(0,25,1))
opar  # this resets the font size
#qplot(dates_h, geom="histogram", binwidth=1)
```
<br>
<br>

```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
#And number of sessions by hour-blocks during the day:
hist(dates_h_forhist, breaks=5, col="lightblue", labels=TRUE, xlim=c(1,25), ylim=c(0,3000), xaxt="n", main="Number of sessions by hour-blocks of the day", ylab="Hour (1=01:00, 24=midnight")
axis(side=1, at=seq(1,25,1), labels=seq(1,25,1))

```

<br>

When we observe the trend in session duration, we find that the majority of each session is between one and ten minutes long, and the majority of users spend less than ten minutes in total per day on the website. We would need to conduct more advanced analytics to determine whether bookings are correlated with longer time spent per day, but given the usage habits for the Airbnb platform reflects 10 minute time frames, from a website/app development perspective, Airbnb should focus on providing an efficient and fasts search experience when provides the information the user needs before she/he moves onto their  next task and lose interest.
<br>
<br>


```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
#This is the distribution of session duration in minutes:
airbnbdata$ts_diff <- airbnbdata$ts_max - airbnbdata$ts_min
airbnbdata$ts_diff <- airbnbdata$ts_diff / 60
airbnbdata$ts_diff <- as.numeric(airbnbdata$ts_diff)
bins <- c(seq(-10,1000,10))
hist(airbnbdata$ts_diff, labels=TRUE, main="Distribution of session duration (min)", col="lightblue", breaks=bins, xlim=c(-10,200), ylim=c(0,6000))
```

<br>


```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
#This is the distribution of total time spent by each user in one day (minutes):
airbnbdata$id_ds <- paste(airbnbdata$id_visitor,airbnbdata$ds)
airbnbdata$flag <- 1

time_user_day <- aggregate.data.frame(airbnbdata$ts_diff, by=list(airbnbdata$id_ds), FUN=sum)
colnames(time_user_day) <- c("ID_and_date", "time")

#time_user_day <-  group_by(airbnbdata, id_ds) %>% summarise(time = sum(ts_diff))
bins <- c(seq(-10,10000,10))
hist(time_user_day$time, labels=TRUE, main="Disbribution of total time (mins) spent per day by each user",col="lightblue", breaks=bins, xlim=c(-10,200), ylim=c(0,2500), xaxt="n", xlab="Total mins spent on Airbnb per day")
axis(side=1, at=seq(-10,200,10), labels=seq(-10,200,10))

```


<br>
<br>

Below we see the relationship between time of day and booking. 
It is interesting to see that the percentage in May appears to be unusally high. Perhaps this is being driven by easier search processes, which may be caused by a greater abundance of available Airbnb rooms. On the contrary this may be caused by a difference in price sensitivity of users during this month. Further data and analysis to assess the underlying drivers of this difference would be interesting as a next step, and may lead to some insights for how to improve the efficiency and ease of the user experience.

<br>
```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
df_cor <- data.frame(dates_m, dates_h, airbnbdata$did_search, airbnbdata$sent_message, airbnbdata$sent_booking_request)
#The group_by function sometimes does not work
df_by_m_book <- df_cor %>% group_by(dates_m) %>% summarise(Sent_booking_request=sum(airbnbdata.sent_booking_request==1), No_booking_request=sum(airbnbdata.sent_booking_request==0))

df_by_m_book$Total_sessions <- df_by_m_book$Sent_booking_request + df_by_m_book$No_booking_request
df_by_m_book$Visit_to_booking_percentage <- df_by_m_book$Sent_booking_request / df_by_m_book$Total_sessions

plot(df_by_m_book$Visit_to_booking_percentage, type="o", main="% of booking requests to total visits, by month", ylab="% bookings to visits", xlab="Month", xaxt="n")
axis(side=1, at=seq(0,12,1), labels=c("","Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"))
```


<br>

##Analysis of booking Device
<br>
##
Number of visits per booking
```{r echo=TRUE, eval=TRUE, tidy=TRUE}
airbnb_visits = nrow(airbnbData)
class(airbnbData)
Visitsperbooking=nrow(airbnbData)/sum(airbnbData$sent_booking_request)
```
<br>
For Looking at Desktop bookings with Chrome

```{r echo=TRUE, eval=TRUE, tidy=TRUE}
airbnb_visits_Chrome = airbnbData[airbnbData$dim_device_app_combo =="Desktop - Chrome", ]
airbnb_bookings_Chrome = sum(airbnb_visits_Chrome$sent_booking_request)
Visit_per_booking_Chrome = nrow(airbnb_visits_Chrome)/airbnb_bookings_Chrome
```
<br>
Number of messages per booking
```{r echo=TRUE, eval=TRUE, tidy=TRUE}
messagesperbooking=sum(airbnbdata$sent_message)/sum(airbnbData$sent_booking_request)
```
<br>
For Looking at Desktop bookings with Chrome
<br>
Number of message per booking

```{r echo=TRUE, eval=TRUE, tidy=TRUE}
airbnb_visits_Chrome = airbnbData[airbnbData$dim_device_app_combo =="Desktop - Chrome", ]
airbnb_bookings_Chrome = sum(airbnb_visits_Chrome$sent_booking_request)
message_per_booking_Chrome = sum(airbnb_visits_Chrome$sent_message)/airbnb_bookings_Chrome
```
<br>
Number of searches per booking
```{r echo=TRUE, eval=TRUE, tidy=TRUE}
searchesperbooking=sum(airbnbData$did_search)/sum(airbnbData$sent_booking_request)
```
<br>
For Looking at Desktop bookings with Chrome
<br>
Number of searches per booking

```{r echo=TRUE, eval=TRUE, tidy=TRUE}
airbnb_visits_Chrome = airbnbData[airbnbData$dim_device_app_combo =="Desktop - Chrome", ]
airbnb_bookings_Chrome = sum(airbnb_visits_Chrome$sent_booking_request)
search_per_booking_Chrome = sum(airbnb_visits_Chrome$did_search)/airbnb_bookings_Chrome
```
<br>
**Summary**

The number of visits/booking is `r Visitsperbooking` and for desktop users this changes to `r Visit_per_booking_Chrome` .

For comparison of number of messages sent. On the whole number of messages per booking are `r messagesperbooking` and for desktop `r message_per_booking_Chrome`.

Similar comparison for the number of searches gives: Total number of searches per booking `r searchesperbooking` and for desktop `r search_per_booking_Chrome`.
<br>

**Device comparison**


To visualise across all the different devices:

Let us create a new table (dataframe) with all the numbers grouped for the devices using the aggregate function

```{r echo=TRUE, eval=TRUE, tidy=TRUE}
Device_data= aggregate.data.frame(airbnbData[,9:11],by=list(airbnbData$dim_device_app_combo), FUN=sum)
Device_number= aggregate.data.frame(airbnbData$entrance, by=list(airbnbData$dim_device_app_combo),FUN=sum)
Device_data$Total=Device_number$x
```
<br>
Now we define per booking metrics for the devices:
```{r echo=TRUE, eval=TRUE, tidy=TRUE}
Device_data$messageperbooking=Device_data$sent_message/Device_data$sent_booking_request
Device_data$searchperbooking=Device_data$did_search/Device_data$sent_booking_request
Device_data$visitsperbooking=Device_data$Total/Device_data$sent_booking_request

```
<br>
Let us look at the table

<br>
We need to remove NA values
```{r echo=TRUE, eval=TRUE, tidy=TRUE}
Device_data[is.na(Device_data)]=0
```
<br>
Let us plot the metrics
```{r echo=TRUE, eval=TRUE, tidy=TRUE}
library(ggplot2)
library(reshape2)
ggplot(Device_data, aes(x=Group.1))+geom_line(aes(y=messageperbooking),colour="blue")+geom_line(aes(y=searchperbooking), colour="grey")+geom_line(aes(y=Visitsperbooking), colour="red")+ylab(label="Metrics")+xlab("Device")

```

